Meta-analytic findings of the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value

### 2021-08-25 docs/revision/manuscript-revised.Rmd
update: fix journal name to reflect change in name

## Future studies
Given that the current meta-analysis failed to support the widely touted assertion of a substantial self-controlled learning benefit [@Sanli2013-xn; @Ste-Marie2019-bw; @Wulf2016-gf], considerations need to be given to the design and research practices for future studies. Registered reports provide one possible path forward [@Caldwell2020-jg]. A registered report involves submitting a research proposal to a two-phase peer-review. The first phase of the review occurs prior to data-collection and is assessed based on the proposed methodology, rationale, and potential contribution. If accepted in principle, researchers commit to carrying out the registered experiment and submitting the results in a final article for the second phase of peer-review. The final article is peer-reviewed for quality and adherence to the registered plan, but accept-reject decisions at this point are not based on the results. In theory, this practice should eliminate *p*-hacking and, for literatures composed entirely of registered reports, publication bias. A number of motor behaviour and/or kinesiology journals have begun adopting registered reports as an option for authors, including the *Human Movement Science*, *Frontiers in Movement Science and Sport Psychology*, *Journal of Sport and Exercise Psychology*, *Journal of Sport Sciences*, and *Registered Reports in Kinesiology*.

>>>>

## Future studies
Given that the current meta-analysis failed to support the widely touted assertion of a substantial self-controlled learning benefit [@Sanli2013-xn; @Ste-Marie2019-bw; @Wulf2016-gf], considerations need to be given to the design and research practices for future studies. Registered reports provide one possible path forward [@Caldwell2020-jg]. A registered report involves submitting a research proposal to a two-phase peer-review. The first phase of the review occurs prior to data-collection and is assessed based on the proposed methodology, rationale, and potential contribution. If accepted in principle, researchers commit to carrying out the registered experiment and submitting the results in a final article for the second phase of peer-review. The final article is peer-reviewed for quality and adherence to the registered plan, but accept-reject decisions at this point are not based on the results. In theory, this practice should eliminate *p*-hacking and, for literatures composed entirely of registered reports, publication bias. A number of motor behaviour and/or kinesiology journals have begun adopting registered reports as an option for authors, including the *Human Movement Science*, *Frontiers in Movement Science and Sport Psychology*, *Journal of Sport and Exercise Psychology*, *Journal of Sport Sciences*, and *Reports in Sport and Exercise (formerly Registered Reports in Kinesiology)*.

### 2021-08-25 docs/revision/manuscript-revised.tex
update: fix journal name to reflect change in name

Given that the current meta-analysis failed to support the widely touted assertion of a substantial self-controlled learning benefit (Sanli, Patterson, Bray, \& Lee, 2013; Ste-Marie, Carter, \& Yantha, 2019; Gabriele Wulf \& Lewthwaite, 2016), considerations need to be given to the design and research practices for future studies. Registered reports provide one possible path forward (Caldwell et al., 2020). A registered report involves submitting a research proposal to a two-phase peer-review. The first phase of the review occurs prior to data-collection and is assessed based on the proposed methodology, rationale, and potential contribution. If accepted in principle, researchers commit to carrying out the registered experiment and submitting the results in a final article for the second phase of peer-review. The final article is peer-reviewed for quality and adherence to the registered plan, but accept-reject decisions at this point are not based on the results. In theory, this practice should eliminate \emph{p}-hacking and, for literatures composed entirely of registered reports, publication bias. A number of motor behaviour and/or kinesiology journals have begun adopting registered reports as an option for authors, including the \emph{Human Movement Science}, \emph{Frontiers in Movement Science and Sport Psychology}, \emph{Journal of Sport and Exercise Psychology}, \emph{Journal of Sport Sciences}, and \emph{Registered Reports in Kinesiology}.

>>>>

Given that the current meta-analysis failed to support the widely touted assertion of a substantial self-controlled learning benefit (Sanli, Patterson, Bray, \& Lee, 2013; Ste-Marie, Carter, \& Yantha, 2019; Gabriele Wulf \& Lewthwaite, 2016), considerations need to be given to the design and research practices for future studies. Registered reports provide one possible path forward (Caldwell et al., 2020). A registered report involves submitting a research proposal to a two-phase peer-review. The first phase of the review occurs prior to data-collection and is assessed based on the proposed methodology, rationale, and potential contribution. If accepted in principle, researchers commit to carrying out the registered experiment and submitting the results in a final article for the second phase of peer-review. The final article is peer-reviewed for quality and adherence to the registered plan, but accept-reject decisions at this point are not based on the results. In theory, this practice should eliminate \emph{p}-hacking and, for literatures composed entirely of registered reports, publication bias. A number of motor behaviour and/or kinesiology journals have begun adopting registered reports as an option for authors, including the \emph{Human Movement Science}, \emph{Frontiers in Movement Science and Sport Psychology}, \emph{Journal of Sport and Exercise Psychology}, \emph{Journal of Sport Sciences}, and \emph{Reports in Sport and Exercise (formerly Registered Reports in Kinesiology)}.
